---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/paulhibbing/AGread.svg?branch=master)](https://travis-ci.org/paulhibbing/AGread)

# AGread

AGread is for automatically detecting the format of .csv data files from ActiGraph accelerometers, and bringing the data into R. It is designed to streamline and standardize the file-reading process, prior to further processing. Thus, it can be used flexibly to develop new methods for handling ActiGraph data, or to invoke existing methods, many of which exist in other R packages (e.g. [PhysicalActivity](https://cran.r-project.org/package=PhysicalActivity) and [TwoRegression](https://cran.r-project.org/package=TwoRegression)), or will soon. 

## Installation

You can install AGread from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("paulhibbing/AGread")
```
