---
output: github_document
---
[![Project Status: Active ? The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Build Status](https://travis-ci.org/paulhibbing/AGread.svg?branch=master)](https://travis-ci.org/paulhibbing/AGread)
[![License](https://img.shields.io/badge/licence-MIT-blue.svg)](https://opensource.org/licenses/MIT)
 
---
 
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/AGread)](https://cran.r-project.org/package=AGread)

---
 
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# AGread

AGread is for bringing ActiGraph sensor data into R. It is designed to streamline and standardize the file-reading process, regardless of which file format is provided (currently supporting `.gt3x` and `.csv`).

AGread can be used flexibly to develop new methods for handling ActiGraph data, or to invoke existing methods, many of which exist in other R packages (e.g. [PhysicalActivity](https://cran.r-project.org/package=PhysicalActivity) and [TwoRegression](https://cran.r-project.org/package=TwoRegression)), or will soon.

New in AGread 1.0.0, `Rcpp` has been invoked to speed up the process of reading `.gt3x` files. There is now documented equivalence between the outcomes of `read_gt3x` and csv reading functions `read_AG__raw` and `read_AG_IMU`.

## Installation

You can install the development version of AGread from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("paulhibbing/AGread")
```

Windows users, make sure you have [Rtools](https://cran.r-project.org/bin/windows/Rtools/) installed before running the above.

Alternatively, AGread v1.0.0 is available on CRAN. Install it with:

```{r cran-installation, eval = FALSE}
install.packages("AGread")
```
